### 2011-02-09 Text/paper.tex
Started the analysis of my files. Found mistake with the determination of diagonal issues

\section{Non-axisymmetric case}
For example according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface. However, one can check whether
completely underresolved interfaces can give something good with the continuous interface methods.
The dimensionalization case is therefore as follows. Instead of starting with the capillary number
simulations we initialize the initial thickness with $2.5$ lattice boltzmann units, change the
pressure gradients through the following numbers:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=
\begin{cases}
1\dots10\mathrm{x}10^{-6}\\
10,15\dots 100 \mathrm{x}10^{-6}
\end{cases}
\end{equation}
After performing the simulations we determine the $R_{axis}$, $R_{diag}$ versus calculated
capillary number
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}.
\end{equation}
To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$,$N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$.
For underresolved schemes, the pressure gradient doesn't work in the way we expect. Therefore, we
take pressure gradient in the following way and later on establish the associated capillary number.
We want to keep track of $R_{diag}$ when the $R_{axis}$ is underresolved. The preliminary results
for the film thickness measured in the middle of the bubble are shown in Fig.
\ref{fig:underresolved:capillaries}. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/underresolved_capillaries.eps}
\caption{The underresolved profiles axis and diagonal radiuses versus capillary numbers. $50$
percent resolution starts from $Ca=1.0$, which is quite high. One can see it's exactly where
radiuses converge instead of $Ca=0.04$. However, one can see from simulations Fig.
\ref{fig:wang:critical:capillary} and Fig.\ref{fig:thickness:variation:ca:ten} the thickness,
especially for Fig.\ref{fig:thickness:variation:ca:ten}, can significantly variate over a bubble
length. \label{fig:underresolved:capillaries}}
\end{figure}

@@

>>>>

\section{Non-axisymmetric case}
As it was indicated before for a quite low capillary number the flow becomes axisymmetric. For
example, according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the axis and diagonal radiuses are $r_h=0.99$ and $r_d=1.1$ respectively.
Therefore the film thickness in the axial direction is  $0.5\%$ of whole channel width to see the
difference. Our previous calculations \cite{kuzmin-binary2d} show that the film thickness should be
 resolved around $40-50$ percent for calculations to be convergent and grid independent. This
condition certainly implies a large grid with the computational high demand. For instance, to
properly simulate the abovementioned example the grid should be as 
$200x200x3000$ nodes. In this section we want to examine the assumption of the underresolved
interface whether it can produce the consistent film thicknesses for low capillary numbers. The
interface occupies around $1-2$ lattice units.

Here we present simulations for the domain of size $52\mathrm{x}52\mathrm{x}1500$ which simulates
the quarter of the channel using the mirror boundary conditions (Section \ref{append:sym}). That
results in the effective grid size as $100\mathrm{x}100\mathrm{x}1500$. The simulation is carried
out with the pressure gradient as:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=1.6\,10^{-6}.
\end{equation}
The initial film thickness was taken as $6$ nodes.

One can see the phase profile in the middle of the bubble in
Fig.\ref{fig:quarter:capillary:capillary01}. The associated capillary number is $0.053$ based on
the calculation of the bubble velocity in the center of the bubble. The radiuses are as follows:
$R_{axis}=0.99$ and $R_{diag}=1.400$. While th  
1.4000714267

\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/}
\end{figure}

\section{Capillary number}
 The
dimensionalization case is therefore as follows. Instead of starting with the capillary number
simulations we initialize the initial thickness with $2.5$ lattice boltzmann units, change the
pressure gradients through the following numbers:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d}x}=
\begin{cases}
1\dots10\mathrm{x}10^{-6}\\
10,15\dots 100 \mathrm{x}10^{-6}
\end{cases}
\end{equation}
After performing the simulations we determine the $R_{axis}$, $R_{diag}$ versus calculated
capillary number
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}.
\end{equation}
To perform simulations we
started with the following parameters as
$k=0.04$,$A=0.04$,$\Gamma=1.0$,$N_x\mathrm{x}N_y\mathrm{x}N_z=52\mathrm{x}52\mathrm{x}750$.
For underresolved schemes, the pressure gradient doesn't work in the way we expect. Therefore, we
take pressure gradient in the following way and later on establish the associated capillary number.
We want to keep track of $R_{diag}$ when the $R_{axis}$ is underresolved. The preliminary results
for the film thickness measured in the middle of the bubble are shown in Fig.
\ref{fig:underresolved:capillaries}. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/underresolved_capillaries.eps}
\caption{The underresolved profiles axis and diagonal radiuses versus capillary numbers. $50$
percent resolution starts from $Ca=1.0$, which is quite high. One can see it's exactly where
radiuses converge instead of $Ca=0.04$. However, one can see from simulations Fig.
\ref{fig:wang:critical:capillary} and Fig.\ref{fig:thickness:variation:ca:ten} the thickness,
especially for Fig.\ref{fig:thickness:variation:ca:ten}, can significantly variate over a bubble
length. \label{fig:underresolved:capillaries}}
\end{figure}

@@

\appendix{Symmetric boundary conditions}
\label{append:sym}
For the memory save we performed the simulation of the quarter of the channel while using the
antisymmetric boundary conditions. In the macroscopic variables the mirror boundary conditions
require to have the same scalar fields, but for velocity only tangential velocities are the same
but perpendicular have the opposite directions. This implies the following in terms of the
macroscopic variables:
\begin{equation}
\rho_B = \rho_F, \quad \phi_B = \phi_F \quad U_{B\tau}=U_{F\tau}, U_{B n}=U_{F n}, 
\end{equation}
 where $B$ and $F$ stand for the boundary and the nearest fluid node, respectively.

In terms of the lattice Boltzmann populations this conditions require the same set of the
populations for the boundary node as for the fluid node. However, the set is mirrored against the
plane of the boundary. This case allows to conserve scalar fields, to have the same tangential
velocities and to have opposite normal velocities. The grid was chosen as 52x52x1500, which is the
effective calculated domain as 100x100x1500 grid nodes.
